Performance Models for Data Transfers: A Case Study with Molecular Chemistry Kernels

### 2019-04-01 Article/article.tex
minor

\usepackage[utf8]{inputenc}
%%\usepackage{amsmath}
%%\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{threeparttable}
\usepackage{graphicx}
\usepackage{color}
\usepackage{paralist}
\usepackage{framed}
%%\usepackage{caption}
\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage{todonotes}

@@

@@

With increasing complexity of hardwares, systems with different memory nodes are ubiquitous in high performance computing (HPC). It is paramount to develop strategies to overlap the data transfers between memory nodes with the computation in order to exploit the full potential of these systems. In this article, we consider the problem of deciding the  order of data transfers between two memory nodes for a set of independent tasks  with the objective to minimize the makespan. We propose an optimal heuristic to obtain the order of data transfers when there is not any restriction on memory limit. We also show that with finite memory capacity obtaining the optimal order of data transfers is an NP-complete problem. We propose several heuristics for this problem and provide analysis of them on traces obtained by running 2 molecular chemistry kernels, namely, Hartree–Fock (HF)  and CCSD on 10 nodes of an HPC system. Our results show that some of our heuristics achieve significant overlap for moderate memory capacities and are very close to the lower bound of makespan.

@@

\section{Related Work}

@@

The problem considered in this paper also can be viewed as a flow shop problem. Communication and computation timings of a task can be considered as processing timings on different machines.  Johnson has provided scheduling strategies for 2 and 3-machine flow shop problems with infinite memory case~\cite{johnson}. 2-machine flow shop problem with finite memory capacity has been proven NP-Complete by Papadimitriou et. al~\cite{Papadimitriou:1980:FSL:322203.322213}. The main difference with the our approach is that they consider unit buffer requirement on 1st machine after job completion. On the contrary, our approach is designed for tasks appearing in scientific workloads whose sizes are highly irregular and memory is acquired before starting the communication.

@@

	\noindent \textbf{Claim} : Order provided by Algorithms~\ref{alg:OrderOfExecutionInfinteMemory} achives the optimal makespan for a set of ready tasks.

	\begin{proof}
		Let us first define some notations which we need for this proof.
%%		\todo[inline]{SKumar: Specify the destination for all notations}
		\begin{align*}
		t : & \text{Time at which data transfer for task A started in original schedule}\\
		S_A : & \text{ Start of computation  time of task A in original schedule}\\
		S_B : & \text{ Start of computation time of task B in original schedule}\\
		S'_A : & \text{ Start of computation time of task A in swapped schedule}\\
		S'_B : & \text{ Start of computation time of task B in swapped schedule}\\
		CM(A) : & \text{ Data transfer time for task A}\\
		CM(B) : & \text{ Data transfer time for task B}\\
		CP(A) : & \text{ Computation time of of task A}\\
		CP(B) : & \text{ Computation time of task B}\\
		\rho : & \text{ ratio of length of task and data transfer time}
		\end{align*}
	\end{proof}

@@

This problem can be expressed as 2-machine flowshop problem with infinite storage, where communication time is the processing time on first machine and computation time is the processing time on second machine and the goal is to minimize the overall makespan. In [], Johnson's algorithm also achieves the optimal makespan but the proof techniques and algorithm are quite different from ours.
	\subsection{Finite Memory}

	In general, order of task execution with input and output data transfers can be 
	viewed as  3-machine flowshop problem, where processing time on 1st machine is 
	input data transfer time,  processing time on 2nd machine is task execution time, 
	processing time on 3rd machine is output data transfer time  and the objective is 
	to minimize the total makespan. This is a well known NP-complete problem.

@@

   	This problem is known to be NP-complete.

@@

\subsection{Static Ordering}
In this class of strategies, we compute the order of both computations and communications in advance based on criteria such as communication time, compute time, accelerated tasks. After computing the order, we follow the same order on computation and communication channels and make sure that at each point in the schedule memory capacity is respected.

In strategy (cite optimal strategy), compute intensive tasks (step 1) are sorted in increasing order of communication times. It allows tasks to utilize the computation channel maximally and make enough space on communication channel to accommodate more communication intensive tasks with maximum overlap. Communication intensive tasks are sorted in decreasing order of communication time, which allows tasks to utilize the gap created on communicated channel. Hence,  in this section, we obtain the orders by sorting tasks based on different combinations of communication and computation times.

@@

@@

In this class of strategy, when communication channel is idle, a task is chosen which satisfies the selection criteria maximally among other tasks. For example, if the selection criteria is to choose a highly compute intensive task, than  we calculate the ratio of compute time and communication time for all tasks, and the task with the  maximum ratio is selected (ties are broken randomly). As we assume that order on both channels is same, hence order on compute channel will follow the order of communication channel.

@@

	\todo[inline]{Machine information and our model}

	We consider a machine called Cascade, available at PNNL, for our experiments. We obtain traces by running  two molecular chemistry applications,  double precision version of Hartree-Fock (HF) and Coupled Cluster Single Double (CCSD) of NWChem package with 4 Uracil molecules input on 10 nodes of this machine. Each node is composed of 16 Intel Xeon E5-2670 cores, hence we use 160 processes for the execution. Each process executes 300-800 tasks.  NWChem takes advantages of a Partitioned Global Address Space Programming Model, Global Arrays (GA), to use shared-memory programming APIs  on distributed memory computers.  Our data transfer model is quite simple and  we consider that all data transfers between each process's local memory and GA memory take the same route. Modeling of different routes of data transfers for the same source-destination pair, bandwidth sharing for different source-destination pairs and network congestion is more challenging and part of our future work. Our model is simple yet it provides insight to the application developers (or runtime system) that  in what-order all data transfer  are issued for the same source-destination pair to maximise communication-computation overlap. Our model is easily adaptable to any source-destination where there is one fixed route between source and destination (such as between CPU and GPU, one copy engine to transfer data from CPU (resp. GPU) to GPU (resp. CPU) ).
	\todo[inline]{More about tiling}
	Both applications mainly perform two types of computations, tensor transpose and tensor contractions.  HF expects to specify a tile size and we set it to 100, so that each core can be efficiently utilize.  CCSD automatically determines tile sizes at different program points based on the input (molecule?).  Hence, HF operates on almost homogeneous tiles while CCSD on heterogeneous tiles.

@@

\begin{figure}[htb]
	\centering
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=.95\linewidth]{../ExperimentalResults/application_properties_hf.pdf}
		\caption{HF workloads}
		\label{fig:hfProperties}
	\end{subfigure}%
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=.95\linewidth]{../ExperimentalResults/application_properties_ccsd.pdf}
		\caption{CCSD workloads}
		\label{fig:ccsdProperties}
	\end{subfigure}
	\caption{HF and CCSD tasks characteristics.}
	\label{fig:ApplicationProperties}
\end{figure}

@@

\subsection{Scheduling In Batches}
In most applications, scheduler can only observe a limited batch of independent tasks. Therefore we organize tasks of each trace file in the group of 100 and apply each heuristic on them consecutively.  Figure~\ref{fig:best_variants_batch} shows performance of the best variants of all categories for both applications. The plots exhibit behavior similar to Figures~\ref{fig:ratio_to_optimal_best_hf} and ~\ref{fig:ratio_to_optimal_best_CCSD}, static+dynamic variants attain maximum communication-computation overlap and outperform other heuristics.
\todo[inline]{SKumar:combine both plots}
\begin{figure}[htb]
	\centering
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=.95\linewidth]{../ExperimentalResults/batch-100/inverse_ratio_to_optimal_hf_batch-best.pdf}
		\caption{Best variants of HF.}
		\label{fig:hf_best_variants_batch}
	\end{subfigure}%
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=.95\linewidth]{../ExperimentalResults/batch-100/inverse_ratio_to_optimal_ccsd_batch-best.pdf}
		\caption{Best variants of CCSD.}
		\label{fig:hf_best_variants_batch}
	\end{subfigure}
	\caption{Best variants of all categories where heuristics are applied in the batches of 100 tasks.}
	\label{fig:best_variants_batch}
\end{figure}

@@

@@

%%	\begin{itemize}
%%		\item Machine description
%%		\item temporary data requirement
%%		\item Description of all kernels (Molecular Chemistry Kernels)
%%		\item Think about results and graphs (Most probably results in $R$ plots)
%%	\end{itemize}

>>>>

\usepackage[utf8]{inputenc}
%%\usepackage{amsmath}
%%\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{threeparttable}
\usepackage{graphicx}
\usepackage{color}
\usepackage{paralist}
\usepackage{framed}
\usepackage{caption}
%%\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage{todonotes}
\usepackage{subfig}

@@

\usepackage{tikz}
\usetikzlibrary{fit,calc,positioning,decorations.pathreplacing,matrix}

@@

With increasing complexity of hardwares, systems with different memory nodes are ubiquitous in high performance computing (HPC). It is paramount to develop strategies to overlap the data transfers between memory nodes with the computation in order to exploit the full potential of these systems. In this article, we consider the problem of deciding the  order of data transfers between two memory nodes for a set of independent tasks  with the objective to minimize the makespan. We propose an optimal heuristic to obtain the order of data transfers when there is not any restriction on memory limit. We also show that with finite memory capacity obtaining the optimal order of data transfers is an NP-complete problem. We propose several heuristics for this problem and provide details about their favorable situations. We present analysis of our heuristics on traces obtained by running 2 molecular chemistry kernels, namely, Hartree–Fock (HF)  and Coupled Cluster Single Double (CCSD) on 10 nodes of an HPC system. Our results show that some of our heuristics achieve significant overlap for moderate memory capacities and are very close to the lower bound of makespan.

@@

\todo[inline]{Add outline of this article (in the end)}
\section{Related Work}

@@

The problem considered in this paper also can be viewed as a flow shop problem. Communication and computation timings of a task can be considered as processing timings on different machines.  Johnson has provided scheduling strategies for 2 and 3-machine flow shop problems with infinite memory capacity~\cite{johnson}. 2-machine flow shop problem with finite memory capacity has been proven NP-Complete by Papadimitriou et. al~\cite{Papadimitriou:1980:FSL:322203.322213}. The main difference with the our approach is that they consider unit buffer requirement on 1st machine after job completion. On the contrary, our approach is designed for tasks appearing in scientific workloads whose sizes are highly irregular and memory is acquired before starting the communication.

@@

	\noindent \textbf{Claim} : Order provided by Algorithm~\ref{alg:OrderOfExecutionInfinteMemory} achives the optimal makespan for a set of ready tasks.
	\todo[inline]{SKumar:rewrite this proof}
	\begin{proof}
		Let us first define some notations which we need for this proof.
%%		\todo[inline]{SKumar: Specify the destination for all notations}
		\begin{align*}
		t : & \text{Time at which data transfer for task A starts in original schedule}\\
		S_A : & \text{ Start of computation  time of task A in original schedule}\\
		S_B : & \text{ Start of computation time of task B in original schedule}\\
		S'_A : & \text{ Start of computation time of task A in swapped schedule}\\
		S'_B : & \text{ Start of computation time of task B in swapped schedule}\\
		CM(A) : & \text{ Data transfer time for task A}\\
		CM(B) : & \text{ Data transfer time for task B}\\
		CP(A) : & \text{ Computation time of of task A}\\
		CP(B) : & \text{ Computation time of task B}\\
		\rho : & \text{ ratio of length of task and data transfer time}
		\end{align*}
	\end{proof}

@@

This problem can be expressed as 2-machine flowshop problem with infinite storage, where communication time is the processing time on first machine and computation time is the processing time on second machine and the goal is to minimize the overall makespan. In ~\cite{GareyJohnson}, Johnson's algorithm also achieves the optimal makespan but the proof techniques and algorithm are quite different from ours.
	\subsection{Finite Memory}

	In general, order of task execution with input and output data transfers can be 
	viewed as  3-machine flowshop problem, where processing time on 1st machine is 
	input data transfer time,  processing time on 2nd machine is task execution time, 
	processing time on 3rd machine is output data transfer time  and the objective is 
	to minimize the total makespan. This is a well known NP-complete problem. 
	\todo{Skumar: Need a citation}
	As stated earlier, we do not consider output data separately in our analysis and assume that output data is zero or stored in a separate buffer. Hence, problem considered in this article is simpler than general 3-machine flowshop problem.

@@

   	This problem is known to be NP-complete.
 	\todo{Skumar: Need a citation}

@@

\subsection{Static Ordering}
In this class of strategies, we compute the order of both computations and communications in advance based on criteria such as communication time, compute time and accelerated tasks. After computing the order, we follow the same order on computation and communication channels and make sure that at each point in the schedule memory capacity is respected.

In Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}, compute intensive tasks (step 1) are sorted in increasing order of communication times. It allows tasks to utilize the computation channel maximally and make enough space on communication channel to accommodate more communication intensive tasks with maximum overlap. Communication intensive tasks are sorted in decreasing order of computation time, which allows tasks to utilize the gap created on communication channel. Hence,  in this section, we obtain the orders by sorting tasks based on different combinations of communication and computation times.

@@

\end{itemize}
\todo[inline]{SKumar: equivalent tikz figure}
\begin{tabular}{|l|l|l|}
\hline
Task & Comm Time & Comp Time\\ \hline
A & 3 & 2\\ \hline
B & 1 & 3\\ \hline
C & 4 & 4\\ \hline
D & 2 & 1\\ \hline
\end{tabular}
	\begin{figure}[htb]
	\centering
%% 	\subfloat[Optimal schedule]{
		\begin{tikzpicture}[decoration={brace, amplitude=5},scale=1, every node/.style={scale=1}]
		\node(t1) at (0,0) {};       		
		\node[above right=0cm and 0cm of t1.mid, draw, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b11) {$B$};

		\node[below right=0cm and 0cm of b11.south east, draw, minimum height=0.5cm, minimum width=3cm,draw,fill=white](b12) {$B$};

		\node[above right=0cm and 0cm of b11.south east, draw, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c11) {$C$};

		\node[below right=0cm and 0cm of c11.south east, draw, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c12) {$C$};

		\node[above right=0cm and 0cm of c11.south east, draw, minimum height=0.5cm, minimum width=3cm,draw,fill=white](a11) {$A$};

		\node[below right=0cm and 0cm of c12.north east, draw, minimum height=0.5cm, minimum width=2cm,draw,fill=white](a12) {$A$};

		\node[above right=0cm and 0cm of a11.south east, draw, minimum height=0.5cm, minimum width=2cm,draw,fill=white](d11) {$D$};

		\node[below right=0cm and 0cm of a12.north east, draw, minimum height=0.5cm, minimum width=1cm,draw,fill=white](d12) {$D$};

%%		\draw[->]	(5,-1)-- (b11.west, b11.south)	;

%%		\draw[->] ([xshift=-0.1cm, yshift=-1cm] b11.south west)--([xshift=13cm, yshift=-1cm] b11.south west);
		\tikzstyle{legend}=[below=0.25, anchor=mid] 	
		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
             -- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.5] {$0$}
             -- ([shift={(1, -0.65)}] t1.mid)node[legend,scale=0.5] {$1$}
             -- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.5] {$4$}
             -- ([shift={(5, -0.65)}] t1.mid)node[legend,scale=0.5] {$5$}
             -- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.5] {$8$}
             -- ([shift={(9, -0.65)}] t1.mid)node[legend,scale=0.5] {$9$}
             -- ([shift={(10, -0.65)}] t1.mid)node[legend,scale=0.5] {$10$}
             -- ([shift={(11, -0.65)}] t1.mid)node[legend,scale=0.5] {$11$}
             -- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.5] {$12$}                                      
              --([shift={(13, -0.65)}] t1.mid) node[right,scale=0.5] {$t$};

      \foreach \x in {0, 1, 4, 5, 8, 9, 10, 11, 12} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);

      \node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$BCAD$};

%%      \node[above right=-1.15cm and -2cm of t1.mid, scale=1, rotate=0] {$Hello BCAD$};

 		\node(t1) at ([shift={(0, -2)}] t1.mid) {};       		
		 \node[above right=0cm and 0cm of t1.mid, draw, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b11) {$B$};

%%  \draw ([yshift=-0.5mm] second0.north)
%%		-- ([yshift=-0.5mm, xshift=0.5mm] second0.north)
%%		-- ([xshift=0.5mm] second0.north);

%%		\node[above left=0.15cm and 0cm of t2.south west, scale=0.5, rotate=0] {$GPU$};
%%		\node[above left=0.15cm and 0cm of t3.south west, scale=0.5, rotate=0] {$CPU$};		
%%		
%%		\tikzstyle{legend}=[below=0.35, anchor=mid] 	
%%		\draw[->] (-0.1, -0.1) -- (0, -0.1)  node[legend,scale=0.5] {$0$} --(1,-0.1) node [legend,scale=0.5] {$1$} --(1.5, -0.1) node[right,scale=0.5] {$t$}; 
%%		
%%		\foreach \x in {0cm, 1cm} \draw (\x, -0.12) -- (\x, -0.08);
%%		%%			To align both figures of subfloat-- an object without drawing at the same depth
%%		\path (-0.1, -0.5) -- (1.5, -0.5);

		\end{tikzpicture}
%%	} %\hspace{0.01\textwidth} %\hfill% or \hspace{5mm} or \hspace{0.3\textwidth}
%%	\subfloat[HP schedule]{
%%		\begin{tikzpicture}[decoration={brace, amplitude=5},scale=1.8, every node/.style={scale=1.8}]
%%		\node(t1) at (0,0) {};      		
%%		
%%		\node[above right=0cm and 0cm of t1.mid, draw, minimum height=0.5cm, minimum width=0.618cm,draw,fill=white](t2) {$Y$};
%%		
%%		\node[above right=0.5cm and 0cm of t2.north west, draw, minimum height=0.5cm, minimum width=1.618cm,draw,fill=white](t3) {$X$};								
%%		
%%		\tikzstyle{legend}=[below=0.35, anchor=mid] 	
%%		\draw[->] (-0.1, -0.1) -- (0, -0.1)  node[legend,scale=0.5] {$0$} --(0.618,-0.1) node [legend,scale=0.5] {$\tfrac{1}{\phi}$} --(1.618,-0.1) node [legend,scale=0.5] {$\phi$} --(2, -0.1) node[right,scale=0.5] {$t$}; 
%%		
%%		\foreach \x in {0cm, 0.618cm, 1.618cm} \draw (\x, -0.12) -- (\x, -0.08);
%%		%%			To align both figures of subfloat -- an object without drawing at the same depth
%%		
%%		\path (-0.1, -0.5) -- (2, -0.5);
%%		
%%		\end{tikzpicture}
%%	} 
	\caption{ \label{fig:staticSchedules} Static.}
\end{figure}

@@

In this class of strategy, when communication channel is idle, a task is chosen which satisfies the selection criteria maximally among other tasks. For example, if the selection criteria is to choose a highly compute intensive task, then  we calculate the ratio of compute time and communication time for all tasks, and the task with the  maximum ratio is selected (ties are broken randomly). As we assume that order on both channels is same, hence order on compute channel will follow the order of communication channel.

@@

%%	\todo[inline]{Machine information and our model}

	We consider a machine called Cascade, available at PNNL, for our experiments. We obtain traces by running  two molecular chemistry applications,  double precision version of Hartree-Fock (HF) and Coupled Cluster Single Double (CCSD) of NWChem package with 4 Uracil molecules input on 10 nodes of this machine. Each node is composed of 16 Intel Xeon E5-2670 cores. NWChem takes advantages of a Partitioned Global Address Space Programming Model, Global Arrays (GA), to use shared-memory programming APIs  on distributed memory computers. GA dedicates one core of each node to handle communication, hence we can view a node as being composed of 15 computational cores. We use 150 processes for each application and obtain 150 trace files. Each process executes around 300-800 tasks. Our data transfer model is quite simple and  we consider that all data transfers between each process's local memory and GA memory take the same route. Modeling of different routes of data transfers for the same source-destination pair, bandwidth sharing for different source-destination pairs and network congestion is more challenging and part of our future work. Our model is simple yet it provides insight to the application developers (or runtime system) that  in what-order all data transfer  are issued for the same source-destination pair to maximise communication-computation overlap. Our model is easily adaptable to any source-destination where there is one fixed route between source and destination (such as between CPU and GPU, one copy engine to transfer data from CPU (resp. GPU) to GPU (resp. CPU) ).
	\todo[inline]{More about tiling}
	Both applications mainly perform two types of computations, tensor transpose and tensor contractions.  HF expects to specify a tile size and we set it to 100, so that each core can be efficiently utilize.  CCSD automatically determines tile sizes at different program points based on the input (molecule?).  Hence, HF operates on almost homogeneous tiles while CCSD on heterogeneous tiles.

@@

 \begin{figure}[htb]
 	%\begin{tabular}{c}
 	\subfloat[HF workloads\label{fig:hfProperties}]{%
		\includegraphics[width=.45\linewidth]{../ExperimentalResults/application_properties_hf.pdf}
 	}%\\
 	\subfloat[CCSD workloads\label{fig:ccsdProperties}]{%
		\includegraphics[width=.45\linewidth]{../ExperimentalResults/application_properties_ccsd.pdf}
 	}%\\
 	%\end{tabular}
	\caption{HF and CCSD tasks characteristics.}
    \label{fig:ApplicationProperties}
 \end{figure}

%%  
%%\begin{figure}[htb]
%%	\centering
%%	\begin{subfigure}{.5\textwidth}
%%		\centering
%%		\includegraphics[width=.95\linewidth]{../ExperimentalResults/application_properties_hf.pdf}
%%		\caption{HF workloads}
%%		\label{fig:hfProperties}
%%	\end{subfigure}%
%%	\begin{subfigure}{.5\textwidth}
%%		\centering
%%		\includegraphics[width=.95\linewidth]{../ExperimentalResults/application_properties_ccsd.pdf}
%%		\caption{CCSD workloads}
%%		\label{fig:ccsdProperties}
%%	\end{subfigure}
%%	\caption{HF and CCSD tasks characteristics.}
%%	\label{fig:ApplicationProperties}
%%\end{figure}

@@

\subsection{Scheduling in Batches}
In most applications, scheduler may only observe a limited batch of independent tasks. Therefore we organize tasks of each trace file in the batch of 100. Last group may have less than 100 tasks. We  apply each heuristic on each group consequently.  Figure~\ref{fig:best_variants_batch} shows performance of the best variants of all categories for both applications. The plots exhibit behavior similar to Figures~\ref{fig:ratio_to_optimal_best_hf} and ~\ref{fig:ratio_to_optimal_best_CCSD}, static+dynamic variants attain maximum communication-computation overlap and outperform other heuristics.
\todo[inline]{SKumar:combine both plots}

 \begin{figure}[htb]
	\subfloat[Best variants of HF.\label{fig:hf_best_variants_batch}]{%
		\includegraphics[width=.45\linewidth]{../ExperimentalResults/batch-100/inverse_ratio_to_optimal_hf_batch-best.pdf}
	}%\\
	\subfloat[Best variants of CCSD.\label{fig:ccsd_best_variants_batch}]{%
		\includegraphics[width=.45\linewidth]{../ExperimentalResults/batch-100/inverse_ratio_to_optimal_ccsd_batch-best.pdf}
	}%\\
	\caption{Best variants of all categories where heuristics are applied in the batches of 100 tasks.}
	\label{fig:best_variants_batch}
 \end{figure}

%%\begin{figure}[htb]
%%	\centering
%%	\begin{subfigure}{.5\textwidth}
%%		\centering
%%		\includegraphics[width=.95\linewidth]{../ExperimentalResults/batch-100/inverse_ratio_to_optimal_hf_batch-best.pdf}
%%		\caption{Best variants of HF.}
%%		\label{fig:hf_best_variants_batch}
%%	\end{subfigure}%
%%	\begin{subfigure}{.5\textwidth}
%%		\centering
%%		\includegraphics[width=.95\linewidth]{../ExperimentalResults/batch-100/inverse_ratio_to_optimal_ccsd_batch-best.pdf}
%%		\caption{Best variants of CCSD.}
%%		\label{fig:ccsd_best_variants_batch}
%%	\end{subfigure}
%%	\caption{Best variants of all categories where heuristics are applied in the batches of 100 tasks.}
%%	\label{fig:best_variants_batch}
%%\end{figure}

@@

%%We also plan to extend our model by taking bandwidth sharing and different possible routes for the same source-destination pair into account.

@@
